|

### 2021-10-13 manuscripts/cprd/supp-materials.Rmd
Pre-final changes to manuscript

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE) # Remove to knit with plots/data
options(scipen = 999)
source(here::here("R/doc_options.R"))
source(here::here("R/helper.R"))

#Load relevant libraries and datasets from the 'outputs' folder

knitr::read_chunk(here::here("R/04-Code-CPRD-Analysis.R"))
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
```

@@

Any changes made to the approved procotol are "Minor amendments" as per the ISAC criteria, specifically falling under the category of "Additional methods to further control for confounding or sensitivity analysis provided these are to be reported as secondary to the main findings".

>>>>

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE) # Remove to knit with plots/data
source(here::here("R/helper.R"))
#Load relevant libraries and datasets from the 'outputs' folder
knitr::read_chunk(here::here("R/05-Code-CPRD-Analysis.R"))
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
```

@@

Any changes made to the approved protocol are "Minor amendments" as per the ISAC criteria, specifically falling under the category of "Additional methods to further control for confounding or sensitivity analysis provided these are to be reported as secondary to the main findings".
